\papertitle

### 2021-03-11 source_separation/paper/paper.tex
made some of the suggested changes, added TODO in Discussion section

	 Orchidea is a framework and set of tools that is currently considered the state-of-the-art for computer-assisted orchestration. Orchidea embeds the target in a feature space and uses a jointly-optimized multi-objective optimization heuristic and constraint solver to find a combination of samples that best match the target~\cite{Cella18, Cella2020}.

@@

	We compare the effectiveness of different source separation methods for the task of orchestration by applying the separation methods to various targets, orchestrating the separated output of the method, and finally comparing this to the orchestration of the target if no separation was performed (see Fig. \ref{fig:full_diagram}). For example, consider a target sound that is a combination of a low droning sound and high-pitched whistle. With separation, these two sounds would be disentangled into two separate sub-targets and each would be individually orchestrated. The separated orchestrations would then be combined to create the solution. This would then be compared to the orchestration if no separation had been performed.

@@

		\subsection{Results}
		The average distances for full target, separated, and ground truth orchestrations are displayed in Table \ref{tab:distances}. These results are the average distance between target and orchestration for 300 different targets. We found that NMF performed the best out of all separation methods, and even outperformed the ground truth orchestrations. TDCN++, Open-Unmix, and NMF performed better than the full target orchestrations, meaning that separating targets using these methods leads to a better orchestration than if no separation is applied.

	\section{Conclusions}\label{sec:conclusions}
	In this paper, we addressed the problem of using source separation as a pre-processing step for computer-assisted orchestration. The results show that performing source separation followed by a static orchestration of each individual sub-target improved the spectral distance between the original target and its orchestrated version in three out of five of the methods tested.

@@

@@

	\section{Future Work}\label{sec:futurework}

	As we stated in Section \ref{sec:conclusions}, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models ourselves with sounds that are more applicable to computer-assisted orchestration. This would be a dataset similar to the samples that make up our targets, instead of the music tracks that the models were trained on.

@@

	Finally, one or multiple of the separation methods we tested should be implemented in Orchidea in order to improve the orchestrations Orchidea is capable of creating. NMF performed the best across the targets we tested on, and therefore makes sense to be added to Orchidea. However, it could also make sense to add one of the musical source spearation methods, such as Open-Unmix, to allow users to choose different methods based on the targets they are orchestrating.

	\begin{acknowledgments}
		Do we have any acknowledgments or should we remove this section?
	\end{acknowledgments}

>>>>

	 Orchidea is a framework and set of tools that is currently considered the state-of-the-art for computer-assisted orchestration. Orchidea embeds the target in a feature space and uses a jointly-optimized optimization heuristic and constraint solver to find a combination of samples that best match the target~\cite{Cella18, Cella2020}.

@@

	We compare the effectiveness of different source separation methods for the task of orchestration by applying the separation methods to various targets, orchestrating the separated output of the method, and finally comparing this to the orchestration of the target if no separation was performed (see Fig. \ref{fig:full_diagram}). Following the previous example, consider a target sound that is a combination of a low droning sound and high-pitched whistle. With separation, these two sounds would be disentangled into two separate sub-targets and each would be individually orchestrated. The separated orchestrations would then be combined to create the solution. This would then be compared to the orchestration if no separation had been performed.

@@

		\subsection{Results}
		The average distances for full target, separated, and ground truth orchestrations are displayed in Table \ref{tab:distances}. These results are the average distance between target and orchestration for 300 different targets. We found that NMF performed the best out of all separation methods, and even outperformed the ground truth orchestrations on average. TDCN++, Open-Unmix, and NMF performed better than the full target orchestrations, meaning that separating targets using these methods leads to a better orchestration than if no separation is applied.

	\section{Discussion}\label{sec:conclusions}
	In this paper, we addressed the problem of using source separation as a pre-processing step for computer-assisted orchestration. The results show that performing source separation followed by a static orchestration of each individual sub-target improved the spectral distance between the original target and its orchestrated version in three out of five of the methods tested. This shows that source separation is a useful pre-processing stage for computer assisted orchestration.

@@

	TODO: say that unsupervised methods can still do well in particular cases where there are not many examples

@@

		\subsection{Future Work}\label{sec:futurework}

		As we stated in Section \ref{sec:conclusions}, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models with sounds that are more appropriate for computer-assisted orchestration.

@@

		Finally, one or multiple of the separation methods we tested should be implemented in Orchidea in order to improve the orchestrations Orchidea is capable of creating.
